%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://raymatsumoto.com/}{\Large Ray Matsumoto}} & Email :
    \href{mailto:ray.a.matsumoto@vanderbilt.edu}{ray.a.matsumoto@vanderbilt.edu} \\
    & Website:
  \href{http://raymatsumoto.com/}{http://www.raymatsumoto.com} \\
    & Mobile: +1-843-475-8628\\
    & GitHub: \href{https://github.com/rmatsum836}{github.com/rmatsum836} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vanderbilt University}{Nashville, TN}
      {Doctorate of Philosophy in Chemical and Biomolecular Engineering}{Aug.
      2016 -- May 2021 (Expected)}
    \resumeSubheading
      {Clemson University}{Clemson, SC}
      {Bachelor of Science in Materials Science and Engineering}{Aug. 2011 -- Dec. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FIRST (Fluid, Interface, Reactions, Structure, and Transport)
      Center}{Nashville, TN}
      {Vanderbilt University}{Jan. 2017 - Present}
      \resumeItemListStart
        \item{Modeled the structure and dynamical behavior of ions in bulk, at
        interfaces, and in nanometer-scale confinement}
        \item{Implemented computational screening over 400+ novel electrolytes to
        understand connections between chemical properties and electrochemical
        performance}
        \item{Implemented a cluster algorithm in python to analyze the structure of
        electrolytes}
        \item{Worked in diverse teams of experimental and computational
            scientists to answer scientific questions}
      \resumeItemListEnd
    \resumeSubheading
      {MoSDeF (Molecular Simulation and Design Framework)}{Nashville,
      TN}
      {Vanderbilt University}{Jan. 2017 - Present}
      \resumeItemListStart
        \item{Developed software for the construction and parametrization of molecular
      models}
        \item{Performed code review, expanded functionality of
            writers for simulation engines, and wrote additional unit
            testing}
      \resumeItemListEnd

    \resumeSubheading
      {Engineering Sales Intern}{Fort Mill, SC}
      {Fitesa}{Summer 2015}
      \resumeItemListStart
        \item{Conducted end product polymer materials analysis to identify sales
            opportunities}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TEACHING-----------------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Undergraduate Lab Mentor}{Nashville, TN}{Vanderbilt University}
      {May 2019 - Present}
      \resumeItemListStart
        \item{Onboarded undergraduate students for a 10-week internship in
            molecular simulation}
        \item{Taught undergraduate students skills in python, unix, and git}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{Nashville, TN}{Vanderbilt University}
      {Aug. 2016 - May 2017}
      \resumeItemListStart
        \item{Chemical Process Principles}
        \item{Modeling and Simulation in Chemical Engineering}
      \resumeItemListEnd

    \resumeSubheading
      {Tutor (Middle School and High School)}{Charleston, SC}{ClubZ! Tutoring
      Services}
      {Jan. 2016 - May 2016}
      \resumeItemListStart
        \item{Tutored multiple students in algebra, chemistry, and AP calculus}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Phase Separation}
      {Open source python library for detecting phase separation in liquid
      solutions through image analysis and image processing}
    \resumeSubItem{Pore-Builder}
      {Python package that interfaces with MoSDeF to construct and parametrize
      graphene slit pores}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
